Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-26 Papers/ms.tex
New mass figure

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are defined by the critical
density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond.
Assuming a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc, one unit corresponds to 6.59$\times 10^{10} M_\odot$.
\label{fig:masses2}}
\end{center}
\end{figure}

@@

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than 88 units
and with 75\% probability it is less than 54 units. Clearly, it is not the
substructure mass over the entire domain that is of interest.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are defined by the critical
density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond. To calculate the masses in solar masses, we assumed a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc.
\label{fig:masses2}}
\end{center}
\end{figure}

@@

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses. As the einstein ring implies a mass of about $5 \times 10^{12}$
solar masses, it is not the substructure mass over the entire domain
that is of interest.
